Communicating with convexity

### 2017-11-13 article_cvxpy.tex
added distance distribution plot

To generate the gain matrix $G$, we randomly sample distances from a given distribution.  For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.  For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.\\

>>>>

To generate the gain matrix $G$, we randomly sample distances from a given distribution.  For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.  For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.  This is illustrated in Figure \ref{fig:dist}.

\begin{figure}[h!]
\includegraphics[width=0.9\linewidth]{distance_distributions.pdf}
\caption{\label{fig:dist}The distance between unpaired transmitters and receivers has a higher variance than paired ones, but on average the unpaired distances are expected to be greater.} 
\end{figure}
